### 2017-02-22 Hhh/Hhh.tex
Some more editing

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least $20\,\GeV$ and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the transverse and longitudinal impact parameters with respect to the primary vertex, $d_{xy}$ and $d_{z}$, must be smaller
than $0.045\,\cm$ and $0.2\,\cm$ respectively. Tight muon identification
criteria and a tight isolation requirement, $I_{\text{rel}}^{\mu} < 0.1$,
 are applied. The hadronic tau must have a \pT~of at least
$20\,\GeV$, $|\eta| < 2.3$, and must have $d_{z} < 0.2\,\cm$. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally,
the combined isolation is required to be
at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-$\Pgm$ discriminator
and the loose working point of the cut-based anti-$\Pe$ discriminator.

@@

After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
The electron should have a \pT~of at least $24\,\GeV$, $|\eta| < 2.1$, and should
satisfy $d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$. The electron must pass the tight
working point of the electron MVA ID discriminator, and the
relative isolation is required to be $I_{\text{rel}}^{\Pe} < 0.1$. The requirements placed on the
hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
where the loose working point is required, and the anti-$\Pe$ discriminator, where the medium
working point of the MVA discriminator is required.

>>>>

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least $20\,\GeV$ and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the transverse and longitudinal impact parameters with respect to the primary vertex, $d_{xy}$ and $d_{z}$, must be smaller
than $0.045\,\cm$ and $0.2\,\cm$ respectively. Tight muon identification
criteria and a tight isolation requirement, $I_{\text{rel}}^{\mu} < 0.1$,
 are applied. The hadronic tau must have a \pT~of at least
$20\,\GeV$, $|\eta| < 2.3$, and must have $d_{z} < 0.2\,\cm$. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally,
the combined isolation is required to be
at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-muon discriminator
and the loose working point of the cut-based anti-electron discriminator.

@@

After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
The electron should have a \pT~of at least $24\,\GeV$, $|\eta| < 2.1$, and should
satisfy $d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$. The electron must pass the tight
working point of the electron MVA ID discriminator, and the
relative isolation is required to be $I_{\text{rel}}^{\Pe} < 0.1$. The requirements placed on the
hadronic tau are similar to those required in the \mutau channel, apart from the anti-muon discriminator,
where the loose working point is required, and the anti-electron discriminator, where the medium
working point of the MVA discriminator is required.

### 2017-02-22 MSSM/MSSM.tex
Some more editing

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of tau leptons will be discussed. The results presented
here correspond to those from an analysis peformed on a dataset collected
during the first half of the 2016 p-p running period of the \ac{LHC}. This dataset
corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-tau pair were studied. The results of this search are 
model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on \xsbr of these two processes, 
the results are interpreted in \ac{MSSM} benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

Signal and background events were generated using
various \ac{MC} event generators. Signal samples
for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\APbottom\phi$
production processes of the \PHiggs or \PHiggsps bosons were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
These samples were produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
This range is slightly wider than the range in which MSSM Higgs sector
benchmark computations are available, $90\,\GeV$--$2\,\TeV$, and 
improves on the mass range of $90\,\GeV$ to $1\,\TeV$ that was studied during Run 1 in the context of \ac{BSM} Higgs searches.
\ac{SM} Higgs boson signal samples are used for the interpretation of the analysis results in 
\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{Powheg} \cite{powheg1,powheg2,powheg3}.

Single-top and \ttbar background samples are generated using \texttt{Powheg},
with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Samples containing both a mixture
of jet multiplicities (`inclusive' samples) and samples with 1,2,3 or 4 jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
only included in the \emu channel, are generated in part with \texttt{MadGraph 5} and in
part with \texttt{MadGraph5\_aMC@NLO}.

@@

The basis of the event selection is to identify \mutau, \etau,
\tautau and \emu pairs. Events are selected first by using a trigger,
followed by additional selection criteria. For the \etau
and \mutau channels we only trigger on the electron or muon. 
While the lepton + hadronic tau cross triggers that are also available
allow for a $3\,\GeV$ ($6\,\GeV$) lower \pT~threshold on the
muon (electron), the benefit of using such a trigger is small: 
most of the signals at high mass, the region of interest in this
analysis, have higher \pT~electrons and muons. This is illustrated
in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
\mutau channel, with the signal normalised to 4000 times its \xsbr 
 at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario overlaid.
In the \emu channel two dedicated electron-muon cross triggers
are used. These have significantly lower \pT~cuts 
on the two leptons than the single lepton triggers. For the 
\tautau channel a di-tau cross-trigger is used.

Because the triggers involving electrons or muons reach 
their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
on the electrons and muons is 1 GeV above the \pT~threshold of the trigger. The
hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
on the hadronic taus in the \tautau channel is $5\,\GeV$ above the trigger \pT~threshold.
In addition, a requirement is made on the $\eta$ of the electrons, muons and
hadronic taus. This selection is driven by the $\eta$ range covered by the tracker and
that is thus used for the reconstruction of the particles. For some of the
channels the used trigger is restricted in $\eta$. If that is the case
then the cut is chosen to align with the trigger restrictions.
As an illustration figure \ref{fig:mt_muonpt}b shows
the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
The signal peaks in the central $\eta$ region.

@@

\subsection{Pair selection and vetos}
\label{sec:mssm_eventsel_pairs}
After applying trigger
requirements, identification criteria and kinematic cuts
more than one possible candidate pair can exist. If
this is the case the pair with the two most isolated candidates
 is chosen, as isolated candidates are less likely 
to be jets misreconstructed
as leptons or hadronic taus.
%If this
%is the case for an event, the pair is chosen as follows:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
%object with raw MVA isolation value nearest to 1.
%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
%and the $\Pgt_h$ for \etau and \mutau channels).
%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
%\end{itemize}

To prevent overlap with other channels, events are rejected
if there are muons and electrons, other than those in the selected pair,
with \pT~$>10\,\GeV$ and passing loose ID and isolation requirements.
This also reduces backgrounds from di-boson events. The application
of these vetos means that the selection of the pair with the
two most isolated candidates is only important where hadronic
taus are concerned, for if there were additional electrons (muons)
the event would not pass the electron (muon) veto.
In addition to these extra electron and muon vetoes, \Zee events are 
reduced in the \etau channel by rejecting events
where an opposite-sign pair of electrons of \pT~$>15\,\GeV$
and passing very loose ID and isolation requirements can be formed. 
In the \mutau channel the contribution from \Zmm events
is reduced in a similar fashion.

\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu tau channel}}
\label{sec:mssm_eventsel_mt}
The trigger only requires a muon at \ac{L1}, while at the level of the \ac{HLT}
loose identification and isolation criteria are applied to this muon.

The offline event selection requires an oppositely charged
muon and hadronically decaying tau, which are well-separated ($\Delta R > 0.5$).
The minimum \pT~of the muon is required to be $23\,\GeV$, with $|\eta| < 2.1$. %due to trigger conditions
Additional ``medium'' identification requirements are placed on the muon, and the impact
parameters of the muon must satisfy $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$. The muon is also
required to be isolated, with $I_{\text{rel}}^{\mu}<0.15$, where the isolation variable
is calculated using a cone size of $\Delta R = 0.4$.

The hadronic tau needs to have a \pT~greater than $30\,\GeV$, $|\eta|<2.3$,
is required to be reconstructed by the HPS algorithm and to pass the medium
working point of the MVA isolation discriminator. The impact parameter $d_{z}$ is
required to be less than $0.2\,\cm$. Finally the hadronic tau is required
to satisfy the very loose working point of the anti-electron discriminator
and the tight working point of the anti-muon discriminator.

The selection on the muon's relative isolation is chosen after comparing
the performance of several isolation variables, using different relative isolation selections.
This was based on a simple \mutau channel
event selection as described above, only varying the isolation requirements.
The selection was optimised based on two figures of merit, both of
which consider \Ztautau as the signal and the other backgrounds
as background. The first figure of merit used is the number of signal events divided by the
square root of the number of background events, $S/\sqrt{B}$, after
the selection. The aim with this figure of merit is to choose
the isolation selection that maximises it. The second figure of merit
is the uncertainty interval on the best-fit value for a maximum-likelihood fit
to the \Ztautau signal strength, which should be minimised by the choice of
isolation selection.

The isolation variables studied include
the $\Delta\beta$ corrected isolation variable analogous
to the one given for electrons in equation \ref{eqn:electron_reliso} with 
isolation cone sizes of $\Delta R$ 0.3 and 0.4. In addition
to this a very similar
variable, which does not just consider charged \ac{PF} hadrons but
also electrons and muons in the isolation sum, is considered. This
variable is also studied for cone sizes of 0.3 and 0.4. Finally,
a relative isolation variable based solely on the \pT~of tracks from the primary
vertex,
\begin{equation}\label{eqn:reltrkiso}
I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{tracks from PV within cone of 0.3 of the muon}}}{p_{\text{T}}^{\mu}}, \end{equation} 
is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
size of the error interval from the maximum-likelihood fit to the \Ztautau signal strength shown in 
\ref{fig:mssm_selection_mt_muons}b. As both figures of merit do not
change so much with varying isolation requirements we can see that this analysis
is not so sensitive to fake, nonisolated muons. The choice of isolation variable is therefore
driven mostly by simplicity and consistency with other \ac{CMS} analyses.

\begin{figure}[h!]
\begin{center}
\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.png}}~\\
\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.png}}
\end{center}
\caption[The $S/\sqrt{B}$ for \Ztautau signal and
the size of the error interval on the best-fit value of a
maximum-likelihood fit to the \Ztautau signal strength, for various 
isolation selections.]{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
the best-fit value of a maximum-likelihood fit to the \Ztautau signal strength,
for various selections of the $\Delta\beta$-corrected
isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
the $\Delta\beta$-corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
the $\Delta\beta$-corrected isolation variable including electrons and muons in the isolation
sum, for a cone size of $\Delta R =0.4$ (upward facing triangles) and $\Delta R =0.3$ (downward facing triangles) and
the tracker-based relative isolation (solid squares).}
\label{fig:mssm_selection_mt_muons}
\end{figure}

A topological selection on the \mT~variable, 
introduced in section \ref{sec:hhh_selection_categories}, is made on 
events in the \mutau channel. This selection and the
choice of hadronic tau isolation working point provide two competing
effects and therefore they are optimised in a 2D-optimisation. 
The pre-fit expected upper limits on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
production with decay into $\Pgt\Pgt$ at several mass points 
in the $90\,\GeV$--$3.2\,\TeV$ range are used as a figure of merit.
Because of the use of such a wide range of signal masses, it
is not possible to choose a selection that is optimal
for every mass point. This is illustrated in figure \ref{fig:mssm_selection_mt_taumt}:
figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on \xsbr for
the gluon fusion production process, for a mass $m_{\phi} = 160\,\GeV$, with
figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9\,\TeV$.
Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
tau isolation working point selection on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$ production process with decay into $\Pgt\Pgt$,
as a function of tau isolation working point (from very loose to very very tight) and
of \mT~selection from \mT~$<20\,\GeV$ to \mT~$<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
\label{fig:mssm_selection_mt_taumt}
\end{figure}
~
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
processes
in the
\mutau channel for an increasingly looser \mT~selection and tau isolation
working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT~$<30\,\GeV$ in green, the medium working point and \mT~$<40\,\GeV$ in red,
the loose working point and \mT~$<50\,\GeV$ in blue and the very loose working point and \mT~$<60\,\GeV$ in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_mt}
\end{figure}

>>>>

\chapter{\texorpdfstring{Search for MSSM \AHtotautau}{Search for MSSM A/H -->tautau}}
\label{chap:mssm}
In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of tau leptons will be discussed. The results presented
here correspond to those from an analysis peformed on a dataset collected
during the first half of the 2016 p-p running period of the \ac{LHC} \cite{CMS-PAS-HIG-16-037}. %This dataset
%corresponds to an integrated luminosity of $12.9\,\invfb$, and the analysis is
%detailed in reference \cite{CMS-PAS-HIG-16-037}. 
The \etau, \mutau, \tautau and \emu final
states of the di-tau pair were studied. The results of this search are 
model-independent upper limits on \xsbr of \PHiggs or \PHiggsps 
production in the gluon fusion ($\Pgluon\Pgluon\phi$) and b-associated ($\Pbottom\Pbottom\phi$) production 
modes (see chapter \ref{chap:theory}) and decay into $\Pgt\Pgt$. 
In addition to the upper limits on \xsbr of these two processes, 
the results are interpreted in \ac{MSSM} benchmark scenarios.
A very similar analysis, not described in detail here,
was performed on a dataset corresponding to $2.3\,\invfb$ collected at $\sqrt{s}=13\,\TeV$ during the 2015 \ac{LHC} p-p running period.  
More information can be found in reference \cite{CMS-PAS-HIG-16-006}.

@@

Signal and background events were generated using
various \ac{MC} event generators. Signal samples
for the $\Pg\Pg \rightarrow \phi$ and $\Pg\Pg \rightarrow \Pbottom\Pbottom\phi$
production processes of the \PHiggs or \PHiggsps bosons were generated using \texttt{PYTHIA 8.1} \cite{pythia81}.
These samples were produced for a range of masses between $90\,\GeV$ and $3.2\,\TeV$.
This range is slightly wider than the range in which MSSM Higgs sector
benchmark computations are available, $90\,\GeV$--$2\,\TeV$, and 
improves on the mass range of $90\,\GeV$ to $1\,\TeV$ that was studied during Run 1 in the context of \ac{BSM} Higgs searches.
\ac{SM} Higgs boson signal samples are used for the interpretation of the analysis results in 
\ac{MSSM} benchmark scenarios. These samples are generated using \texttt{POWHEG} \cite{powheg1,powheg2,powheg3}.

Single-top and \ttbar background samples are generated using \texttt{POWHEG},
with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Samples containing both a mixture
of jet multiplicities (`inclusive' samples) and samples with one, two, three or four jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
with \texttt{MadGraph5\_aMC@NLO}.

@@

The basis of the event selection is to identify \mutau, \etau,
\tautau and \emu pairs. Events are selected first by using a trigger,
followed by additional selection criteria. For the \etau
and \mutau channels events are selected by only triggering on the electron or muon. 
While the lepton + hadronic tau cross-triggers that are also available
allow for a $3\,\GeV$ ($6\,\GeV$) lower \pT~threshold on the
muon (electron), the benefit of using such a trigger is small: 
most of the signals at high mass, the region of interest in this
analysis, have higher \pT~electrons and muons. This is illustrated
in figure \ref{fig:mt_muonpt}a, which shows the \pT~of muons in the
\mutau channel. The signal is overlaid, with a normalisation of 4000 times its \xsbr 
 at \mA~$=1\,\TeV$ and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod}+}$ scenario.
In the \emu channel two dedicated electron-muon cross-triggers
are used. These have significantly lower \pT~cuts 
on the two leptons than the single lepton triggers. For the 
\tautau channel a di-tau trigger is used.

Because the triggers involving electrons or muons reach 
their maximum efficiency as a function of \pT~quickly, the offline \pT~cut
on the electrons and muons is $1\,\GeV$ above the \pT~threshold of the trigger. The
hadronic tau efficiency turns on much more slowly, and therefore the offline \pT~cut
on the hadronic taus in the \tautau channel is $5\,\GeV$ above the trigger \pT~threshold.
In addition, a requirement is made on the $\eta$ of the electrons, muons and
hadronic taus. This selection is driven by the $\eta$ range covered by the tracker and
so the range that is used for the reconstruction of the particles. For some of the
channels the trigger that is used is restricted in $\eta$. If that is the case
the cut is chosen to be the same as the trigger restrictions.
As an illustration figure \ref{fig:mt_muonpt}b shows
the $\eta$ distribution for electrons in the \etau channel, again with the signal overlaid.
The signal peaks in the central $\eta$ region.

@@

\subsection{Pair selection and vetoes}
\label{sec:mssm_eventsel_pairs}
After applying trigger
requirements, identification criteria and kinematic cuts
more than one possible candidate pair can exist. If
this is the case the pair with the two most isolated candidates
 is chosen, as isolated candidates are less likely 
to be jets mis-reconstructed
as leptons or hadronic taus.
%If this
%is the case for an event, the pair is chosen as follows:
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item Prefer the pair with most isolated candidate 1 (muon for \mutau and \emu channels,
%electron for \etau channel, either of the $\Pgt_h$s in \tautau channel). For electrons
%and muons this means the object with the smallest relative isolation value is preferred, for $\Pgt_h$s the
%object with raw MVA isolation value nearest to 1.
%\item If the isolation of candidate 1 is the same in both pairs, prefer the pair with highest candidate 1 \pT.
%\item If the \pT~of candidate 1 is the same in both pairs, prefer the pair with most isolated
%candidate 2 (e for the \emu channel, the other $\Pgt_h$ for the \tautau channel, 
%and the $\Pgt_h$ for \etau and \mutau channels).
%\item If the isolation of candidate 2 is the same in both pairs, prefer the pair with highest candidate 2 \pT.
%\end{itemize}

To prevent overlap with other channels, events are rejected
if there are muons or electrons, other than those in the selected pair,
with \pT~$>10\,\GeV$ and passing loose ID and isolation requirements.
This also reduces backgrounds from di-boson events. The application
of these vetoes means that the selection of the pair with the
two most isolated candidates is only important where hadronic
taus are concerned, for if there were additional electrons (muons)
the event would not pass the electron (muon) veto.
In addition to these extra electron and muon vetoes, \Zee events are 
reduced in the \etau channel by rejecting events
where an opposite-sign pair of electrons of \pT~$>15\,\GeV$
and passing very loose ID and isolation requirements can be formed. 
In the \mutau channel the contribution from \Zmm events
is reduced in a similar fashion.

\subsection{\texorpdfstring{Event selection in the \mutau channel}{Event selection in the mu tau channel}}
\label{sec:mssm_eventsel_mt}
The trigger only requires a muon at \ac{L1}, to which loose identification and
isolation criteria are applied at the level of the \ac{HLT}

The offline event selection requires an oppositely charged
muon and hadronically decaying tau, which are separated by $\Delta R > 0.5$.
The muon is required to have \pT~$> 23\,\GeV$, and $|\eta| < 2.1$. %due to trigger conditions
Additional ``medium'' identification requirements are placed on the muon, and the impact
parameters must satisfy $d_{xy}<0.045\,\cm$ and $d_{z}<0.2\,\cm$. The muon is also
required to be isolated, with $I_{\text{rel}}^{\mu}<0.15$, where the isolation variable
is calculated using a cone size of $\Delta R = 0.4$.

The hadronic tau needs to have \pT~$>30\,\GeV$ and $|\eta|<2.3$.
It is required to be reconstructed by the HPS algorithm and to pass the medium
working point of the MVA isolation discriminator. The impact parameter $d_{z}$ is
required to be less than $0.2\,\cm$. Finally the hadronic tau is required
to satisfy the very loose working point of the anti-electron discriminator
and the tight working point of the anti-muon discriminator.

The selection on the relative isolation of the muon is chosen after comparing
the performance of several isolation variables, using different relative isolation selections.
This was based on a simple \mutau channel
event selection as described above, with only the isolation being varied.
The selection was optimised based on two figures of merit, both of
which consider \Ztautau, instead of the Higgs processes, as the signal.
The first figure of merit used is the number of signal events divided by the
square root of the number of background events, $S/\sqrt{B}$, after
the selection. The aim is to identify 
the isolation selection that maximises $S/\sqrt{B}$. The second figure of merit
is the uncertainty interval on the best-fit value for a maximum-likelihood fit
to the \Ztautau signal strength, which should be minimised by the choice of
isolation selection.

The isolation variables studied include
the $\Delta\beta$ corrected isolation variable analogous
to the one given for electrons in equation \ref{eqn:electron_reliso} with 
isolation cone sizes of 0.3 and 0.4 in $\Delta R$. In addition
to this a very similar
variable, which does not just consider charged \ac{PF} hadrons but
also electrons and muons in the isolation sum, is considered. This
variable is also studied for cone sizes of 0.3 and 0.4. Finally,
a relative isolation variable based solely on the \pT~of tracks from the primary
vertex,
\begin{equation}\label{eqn:reltrkiso}
I_{\text{trk}} = \frac{\Sigma p_{\text{T}}^{\text{tracks from PV within cone of 0.3 of the muon}}}{p_{\text{T}}^{\mu}}, \end{equation} 
is studied. The $S/\sqrt{B}$ for the different isolation variables is shown in figure \ref{fig:mssm_selection_mt_muons}a, with the
size of the error interval from the maximum-likelihood fit to the \Ztautau signal strength shown in 
\ref{fig:mssm_selection_mt_muons}b. Both figures of merit do not
change significantly when varying the isolation requirements meaning that this analysis
is not so sensitive to fake, non-isolated muons. The choice of isolation variable is therefore
driven mostly by simplicity and consistency with other \ac{CMS} analyses.

\begin{figure}[h!]
\begin{center}
\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.png}}~\\
\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.png}}
\end{center}
\caption[The $S/\sqrt{B}$ for \Ztautau signal and
the size of the error interval on the best-fit value of a
maximum-likelihood fit to the \Ztautau signal strength, for various 
isolation selections.]{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
the best-fit value of a maximum-likelihood fit to the \Ztautau signal strength,
for various selections of the $\Delta\beta$-corrected
isolation variable with a cone size of $\Delta R = 0.4$ (solid circles) and $\Delta R = 0.3$ (open circles),
the $\Delta\beta$-corrected isolation variable including electrons and muons in the isolation
sum, for a cone size of $\Delta R =0.4$ (upward facing triangles) and $\Delta R =0.3$ (downward facing triangles) and
the tracker-based relative isolation (solid squares).}
\label{fig:mssm_selection_mt_muons}
\end{figure}

A topological selection on the \mT~variable, 
introduced in section \ref{sec:hhh_selection_categories}, is made on 
events in the \mutau channel. This selection and the
choice of hadronic tau isolation working point provide two competing
effects and therefore they are optimised simultaneously.
The ``pre-fit'' expected upper limits, determined without the fit
to the real observed data, on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
production with decay into $\Pgt\Pgt$ at several mass points 
in the $90\,\GeV$--$3.2\,\TeV$ range are used as a figure of merit.
Because of the use of such a wide range of signal masses, it
is not possible to choose a selection that is optimal
for every mass point. This is illustrated in figure \ref{fig:mssm_selection_mt_taumt}:
figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on \xsbr for
the gluon fusion production process, for a mass $m_{\phi} = 160\,\GeV$, with
figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9\,\TeV$.
Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
tau isolation working point selections on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160\,\GeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
\subfloat[$m_{\phi} = 2.9\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption[Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$
production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
working point and \mT~selection, for two mass points.]{Pre-fit expected limit on \xsbr for the $\Pg\Pg\phi$ production process with decay into $\Pgt\Pgt$,
as a function of tau isolation working point (from very loose to very very tight) and
of \mT~selection from \mT~$<20\,\GeV$ to \mT~$<40\,\GeV$, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for (a) $m_{\phi} = 160\,\GeV$ and (b) $m_{\phi} = 2.9\,\TeV$. The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
\label{fig:mssm_selection_mt_taumt}
\end{figure}
~
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
\subfloat[$\Pbottom\Pbottom\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
\end{center}
\caption[Pre-fit expected limits on \xsbr for the $\Pg\Pg\phi$ and $\Pbottom\Pbottom\phi$
processes
in the
\mutau channel for an increasingly looser \mT~selection and tau isolation
working point.]{Pre-fit expected limits on \xsbr in the \mutau channel for (a) $\Pg\Pg\phi$ and
(b) $\Pbottom\Pbottom\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT~$<30\,\GeV$ in green, the medium working point and \mT~$<40\,\GeV$ in red,
the loose working point and \mT~$<50\,\GeV$ in blue and the very loose working point and \mT~$<60\,\GeV$ in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_mt}
\end{figure}
